Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2019-12-03 xrb/paper.tex
addresses marginpar

Table~\ref{table:diffusion} shows the L-inf error against the analytic
solution for the diffusion test problem.  The tests were run in two
fashions: no AMR, and AMR with one level of refinement (a jump of
$2\times$).  In both cases we see second-order convergence of the
error.\MarginPar{This would be clearer if there was a third column showing the ratios of the errors?}  Figure~\ref{fig:diffusion} shows the temperature at the end of
the simulation of the $64\times 128$ base grid plus one level of
refinement simulation, with the grids shown to illustrate where the
refinement jump is.

>>>>

Table~\ref{table:diffusion} shows the L-inf error against the analytic
solution for the diffusion test problem.  The tests were run in two
fashions: no AMR, and AMR with one level of refinement (a jump of
$2\times$).  In both cases we see second-order convergence of the
error.  Figure~\ref{fig:diffusion} shows the temperature at the end of
the simulation of the $64\times 128$ base grid plus one level of
refinement simulation, with the grids shown to illustrate where the
refinement jump is.
